---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pkgattrs

The goal of pkgattrs is to get information on the contents of an R package. So far, we can obtain a summary of functions available in one or more packages using the `get_pkg_fcn_info()` function. Here is an example where function information is obtained from the `pkgattrs` and `blastula` packages.

```{r}
library(pkgattrs)

fcn_info <-
  get_pkg_fcn_info(
    from_github("rich-iannone/pkgattrs"),
    from_github("rich-iannone/blastula"))
```

The resulting tibble contains a line for every function, which file each is located, starting/ending line numbers, and more.

```{r paged.print=FALSE}
fcn_info
```

## Installation

You can install pkgattrs from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("rich-iannone/pkgattrs")
```

