---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pkgattrs

The goal of pkgattrs is to get information on the contents of an R package. So far, we can obtain a summary of functions available in one or more packages using the `get_pkg_fcn_info()` function. Here is an example that gets information about the functions in the `pkgattrs` and `blastula` packages that are hosted on GitHub.

```{r}
library(pkgattrs)

fcn_info <-
  get_pkg_fcn_info(
    from_github("rich-iannone/pkgattrs"),
    from_github("rich-iannone/blastula"))
```

The resulting tibble contains the following information in each record:

- the package name (`pkg_name`)
- the function name (`fcn_name`)
- the file that contains the function (`r_file`)
- the line number in `r_file` where the function starts (`ln_start`) and ends (`ln_end`)
- the number of lines used for the function (`lines`)
- whether the function is exported or not (`exported`)
- the number of package functions that are called in `fcn_name` (`n_pkg_fcns_called`)
- a list column with the names of the package functions called in `fcn_name` (`pkg_fcns_called`)

```{r}
fcn_info
```

## Installation

You can install pkgattrs from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("rich-iannone/pkgattrs")
```

